Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
using the example of Sec 3.1 to explain prop> in step by step manner.
adding more explanations to Sec 4.1.2.

\subsection{Doctest and Haddock}

@@

\noindent Of course, we allowed quantified properties by using closed
lambda terms.
Type signatures can be specified for each parameter:

>>>>

\subsection{Doctest and Haddock}
\label{sec:doctest-haddock}

@@

\noindent Of course, we allowed quantified properties by using closed
lambda terms. The property example in Section~\ref{sec:doctest-haddock}
can be written as follows:

\begin{quote}
\small
\begin{alltt}
prop> \verb|\|x -> null (takeExtension x) == \(\hookleftarrow\)
            not (hasExtension x)
\end{alltt}
\end{quote}

\noindent If a default type is not suitable, expression type--signatures can be specified for each parameter:
